\chapter{Acknowledgments}

First of all, I want to thank Prof.~Dr.~Dr.~Wolfgang Rhode and Dr.~Dirk Wiedner for giving me the opportunity to
write this thesis. I'd also like to thank the members of the E5b working group, who immediately
made me feel welcome and who were never shy to answer questions or give me advice or feedback.
Whether over lunch or on other occasions, it was always a pleasure talking to and getting to know
every one of them.

I want to especially thank Noah Biederbeck, Max Linhoff and Lukas Nickel, who were my advisors
during the course of the thesis and who would always help me whenever I was stuck. I also want to
thank Jonas Hackfeld, who more than once helped me out with questions I had.

For the good time we had, I also want to thank my office mates Lukas Beiske and Fabian Schierok,
who, whenever they were in the office, would always be open to discussions about problems any of
us would encounter. This exchange helped me develop new ideas and improve my programming skills.

To all the people who have proofread my thesis, I would like to thank you for your help. This includes
my advisors Noah, Max and Lukas as well as Jonas, but also Vanessa Sulaiman, Christopher Wittler,
Jasmin Bedow and Henrik Hegenberg.

I would also like to thank my family and friends for their support during my time here and their
understanding if I---occasionally---had to spend more time with this work than anticipated.

Finally, I would like to thank Vanessa for everything. Without your support, I would most likely not have
come this far.